# knitron: knitr + IPython + matplotlib
Use IPython in knitr!

Knitron brings the power of IPython and matplotlib to [knitr](http://yihui.name/knitr/).

Currently a work in progress; it is already usable.

## Installation

```r
library(devtools)
install_github("knitron", "fhirschmann")
```

## Usage

```r
library(knitron)
```

That's it! Now you can use IPython in knitr using the `engine = 'ipython'` option
(see the [source code](https://raw.githubusercontent.com/fhirschmann/knitron/master/README.Rmd)
of this page for an example).

Knitron brings workspace-like interaction for Python to knitr, so you can define
a variable in one chunk

```{r, engine = 'ipython'}
x = 5
```

and access it in a following chunck

```{r, engine = 'ipython'}
5 + 1
```

### Supported Features and Limitations

Most of the original knitr chunk options are supported, including

- `fig.path`
- `fig.width` and `fig.height`
- `dpi`
- `dev` ('pdf' for LaTeX and 'png' for HTML/markdown)

However, there are limitations to some options:

- fig.show only supports 'hold', i.e. all figures are placed at the end of the code chunk

## Examples

```{r example1, engine = 'ipython'}
import numpy as np
x = np.linspace(0, 2 * np.pi, 100)
y1 = np.sin(x)
y2 = np.sin(3 * x)
plt.fill(x, y1, 'b', x, y2, 'r', alpha=0.3)
```

```{r example2, engine = 'ipython'}
L = 6
x = np.linspace(0, L)
ncolors = len(plt.rcParams['axes.color_cycle'])
shift = np.linspace(0, L, ncolors, endpoint=False)
for s in shift:
    plt.plot(x, np.sin(x + s), 'o-')
```
