# knitron: knitr + IPython + matplotlib

Knitron brings the power of IPython and matplotlib to [knitr](http://yihui.name/knitr/).

Currently a work in progress; it is already usable.

NOTE: I wrote this for an older version of IPython where the `IPython.kernel` module was
still present. The API seems to have changed and I'll write a version for the new IPython
API when I have time to do so.


## Installation

```r
library(devtools)
install_github("knitron", "fhirschmann")
```

## Usage

```r
library(knitron)
```

That's it! Now you can use IPython in knitr using the `engine = 'ipython'` option
(see the [source code](https://raw.githubusercontent.com/fhirschmann/knitron/master/README.Rmd)
of this page for an example).

Knitron brings workspace-like interaction for Python to knitr, so you can define
a variable in one chunk

```{r, engine = 'ipython'}
x = 5
```

and access it in a following chunck

```{r, engine = 'ipython'}
5 + 1
```

### Supported Features and Limitations

Most of the original knitr chunk options are supported, including

- `fig.path`
- `fig.width` and `fig.height`
- `dpi`
- `dev` ('pdf' for LaTeX and 'png' for HTML/markdown)

However, there are limitations to some options:

- fig.show only supports 'hold', i.e. all figures are placed at the end of the code chunk

IPython's magic functions are supported too, of course. But there are
some limitations, i.e. magic functions that insert text into the IPython
shell like `%load` without executing them don't work. Likewise, magics
that are meant for interaction use like `%man` and `%edit` cannot work in
knitr.

## Examples

## IPython

```{r, engine = 'ipython'}
from time import sleep

%time sleep(0.5)
```

```{r, engine = 'ipython'}
%whos
```

### Matplotlib

```{r example1, engine = 'ipython'}
import numpy as np
x = np.linspace(0, 2 * np.pi, 100)
y1 = np.sin(x)
y2 = np.sin(3 * x)
plt.fill(x, y1, 'b', x, y2, 'r', alpha=0.3)
```

```{r example2, engine = 'ipython'}
L = 6
x = np.linspace(0, L)
ncolors = len(plt.rcParams['axes.color_cycle'])
shift = np.linspace(0, L, ncolors, endpoint=False)
for s in shift:
    plt.plot(x, np.sin(x + s), 'o-')
```

## Sympy

```{r, engine = 'ipython'}
import sympy as sm

x, y, z = sm.symbols("x y z")
sm.solve([x * y - 7, x + y - 6], [x, y])
```

Of course, you could also use `sm.latex` and `results = 'asis'` in
TeX documents.
